HPC--101\\Onboarding

### 2018-05-08 hpc_101/sections/07_policies.tex
added age_check instructions

>>>>

\begin{frame}
  \frametitle{How to check file age for purge}
  A tool is available on the cluster called age\_check.  This tool will list all files that are older than the defined date you set.
\begin{semiverbatim}\tiny \texttt
  $[$root@login-0001 \ctilde$]$\$ age\_check -h

  Usage:
  age\_check [-s] [-z] [-d] [-f] [-a <age cutoff>] [-p <path]

  Options:

  -s -- Sort output

  -d -- display creation date per file

  -z -- display size in bytes per file

  -f -- Do not exclude files between 1 byte and 1 MB

  -a age -- Lists files that were created at least age days ago (default is 20 days)

  -p path -- Directory to check in (default is /lus/scratch/root)

  Example:
  age\_check -a 30

\end{semiverbatim}

\end{frame}
